Screening Sinkhorn Algorithm for Regularized Optimal Transport

### 2019-05-19 tex/v3/section_5_numeric_expes.tex
new figure

\subsection{Setup}
the lbfgs is the one of scipy

@@

In this subsection, we analyse the impact of using \emph{Screenkhorn}
instead of Sinkhorn in a complex machine learning pipeline. Our two applications
are a dimensionality reduction technique, denoted as Wasserstein Discriminant Analysis (WDA), based on Wasserstein distance approximated
through Sinkhorn divergence \cite{flamary2018WDA} and a domain-adaptation using optimal transport mapping \cite{courty2017optimal}, named OTDA. For both applications, we have based our code
on the ones of POT \cite{flamary2017pot} and just replaced the Sinkhorn function call with a Screenkhorn one. We have considered the POT's default Sinkhorn stopping criterion parameters and for Screenkhorn, the LBFGS algorithm is stopped when the 
largest component of the projected gradient is smaller than $10^{-6}$, when the
number of iterations of number of objective function evaluations reach $10^{5}$. For all
applications, we have set $\eta=1$.

>>>>

In this section, we present some numerical analyses of our
\emph{Screenkhorn} algorithm and show how it behaves when
integrated into some complex machine learning pipelines.

\subsection{Setup}

We have implemented our Screenkhorn in Python and used the LBFGS of
Scipy. Regarding the machine-learning based comparison, we have based our code
on the ones of POT \cite{flamary2017pot} and just replaced the Sinkhorn function call with a Screenkhorn one. We have considered the POT's default Sinkhorn stopping criterion parameters and for Screenkhorn, the LBFGS algorithm is stopped when the 
largest component of the projected gradient is smaller than $10^{-6}$, when the number of iterations of number of objective function evaluations reach $10^{5}$. For all applications, we have set $\eta=1$.

@@

In this subsection, we analyse the impact of using \emph{Screenkhorn}
instead of Sinkhorn in a complex machine learning pipeline. Our two applications
are a dimensionality reduction technique, denoted as Wasserstein Discriminant Analysis (WDA), based on Wasserstein distance approximated
through Sinkhorn divergence \cite{flamary2018WDA} and a domain-adaptation using optimal transport mapping \cite{courty2017optimal}, named OTDA.
